\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-27 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Changement texte + online

\textbf{JH : I WOULD DELETE EVERYTHING FROM `` It is true that"}

@@

Our analysis of transportation costs consists of exploiting the difference between commodity-level export and import prices, as in \cite{hummels2007}. The database we use to construct our measure of transport costs comes from the US annual ``Imports of Merchandise'' provided by the US Census Bureau, spanning 1974 to 2019 (details on the database provided in Appendix \ref{app:data}). We first use customs values, quantities and freight costs to recover free alongside ship (fas) and cost-insurance-freight (cif) prices, by good, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob (free on board) price rather than the fas price. While both terms are closely related (see more details in Appendix \ref{app:data}), the US Foreign Trade Statistics reports fas prices.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight, both items being conditional to the transport mode; in other words, it is the price for one kg of the goods net of transportation costs, by transport mode.\footnote{One may be concerned by the fact that unit prices are calculated as the value divided by the shipping weight, rather than to the quantity (the number) of goods. This is due to the fact that in the Census data, information on the quantity of goods is not mode-specific. We yet provide a robustness check where unit values are built as the ratio between value and quantity of goods per observation, on a specific sub-sample restricted to US imports flows that only use one single transport mode. \textbf{See Section D.4 in the Online Appendix}. \textbf{LE METTRE EN FOOTNOTE ME PARAIT LEGER, POINT IMPORTANT DU REFERE 1 + bcp de footnotes. Le remonter dans le corps PPL?}} The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. By construction higher than 1, the variable provides a measure of transport costs as a proportion of the goods' price, an ad-valorem equivalent. This is quite a standard and widespread strategy, as emphasized by \cite{anderson_wincoop_jel}.

@@

As detailed below, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. This drives us to estimate international transport costs at the 3-digit classification level, exploiting heterogeneity between products at the SITC-5 classification level. Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin (hence, around 400 fixed effects). We ensure the robustness of these results by conducting two types of alternative estimates: \textit{i),} within each 3-digit sector, exploiting heterogeneity between HS-10 products. Notice that this can be done from 1989 onwards for which HS-10 data are available; \textit{ii),} running the estimation at the 4-digit sector level (still with 5-digit products) for some selected years. The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2019. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the results obtained for the benchmark 3-5 sector-product classification levels and those considering either the 3-10 and 4-5 ones (See Table \ref{tab:summary_results} and Appendix \ref{app:4digit} for the 4-5 results and Table \ref{tab:baseline10}, Section \ref{sec:robustness} for the 3-10 estimation results). \textbf{ADD 10-3 RESULTS TO BE DONE}

@@

\paragraph{The share of additive costs: Time dynamics} As next step, we investigate whether additive costs are a long-lasting, i.e. a structural phenomenon. Figure \ref{fig:part_cout_additif} reports the share of additive costs in total transport costs on a yearly basis, in both air and vessel transport, based on the weighted-mean values $\widehat{t}/\widetilde{p}$ and $\widehat{\tau}$.
.

@@

Three main comments can be made. First, the subset of large trade flows we are considering (around 8\% of the observations of our initial sample, but the vast majority of the total value of aggregated trade (an annual mean of 68\%) involve a higher share of additive costs: between 48\% and 55\% of total costs on average, versus 30\% to 44\% on the whole sample.
%JH: la phrase suivante est en contradiction avec celle qui suit encore juste après: "Second, assuming that country/product fixed effects are separable in these two dimensions tends to overestimate the value and the share of the additive costs."
Second, both models provide a similar quality of fit of the regression (once we take into account the number of right-hand-side variables) as the AIC criteria display very close values in both models (conditional on transport mode). Third, crucially for this robustness check the estimated values remain of similar magnitude under both separability and non-separability assumptions.\footnote{We also run two other robustness checks: \textit{i}) comparing the chronolgy of results and \textit{ii}) reporting the histogram of the distribution for $\beta$ over the triplet $(i,k,t)$, which confirm the robustness of the results. These results are reported in the Online Appendix, respectively in sections C \textbf{Bah non. Il n’y a pas de 3/10 dans la section C ? Je crois qu’il n’y a que D.2. avec quelque chose}and D.2. Bon, et je ne sais pas très bien en quoi les histogrammes nous aident ; je ne comprends } %, even if one can note that under the separability assumption, the share of additive costs seems slightly biased upward, at least for averages over the period. The picture is reversed for medians

@@

\begin{figure}[htbp]
\caption{Transport cost time trends: robustness to IV procedure}
\label{fig:comp_IV_SITC5}
\begin{center}
\includegraphics[height=8cm]
{scatter_chronology_baseline_IV_ref1_y_5_3.png}
\end{center}
\end{figure}

\textbf{LP: Guillaume, changer les legendes de la figure enlever beta, mettre en positif la part des additifs et ajouter legende en ordonnee...}
%However, we consider as a reasonable assumption that the exporting firm cannot influence the international transport cost sector, that would imply a causal effect of the firm's prices on the transport costs value, except in the choice between air and vessel transport (that is beyond our scope of analysis).
%Otherwise stated, conditional to an export price and a transport mode, the gap between the export price declared to the custom data and the import price recorded by the US administration is beyond the firm's control.
%In this respect, we are confident that our estimation strategy is immune from endogeneity problems.

@@

Yet, as Table \ref{tab:baseline10} and 	Figure \ref{fig:robustness_to_agregation} show, the results are very similar when using 10-digit product and 5-digit products. If anything, the $\beta$ seems on average slightly higher when estimated based on a 3 (sector)-10(product) database, indicating a (small) downward bias in our estimates of additive costs. But overall, no major difference arises both regarding levels and trends - results are especially very close for the Air transportation mode. This has important implications for the exercise performed in section \ref{sec:theory}: welfare gains computations should not be significantly affected by our use of 5 (sector)-5 (product) digit data. This is consistent with e.g. \citet{Giri_et_al2021}, who show that sectoral heterogeneity does not always lead to an increase in the gains from trade.

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: Robustness to aggregation (2005-2019)} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10.tex}
	\input{Table_baseline10_reshaped.tex}
	\begin{tablenotes}
		\scriptsize
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
        \item Transport costs expressed in \% of the fas price (except for $\widehat{t}$ expressed in USD.
		%\item \textbf{Model (A): With ad-valorem transport costs only}
		\item Model (B): With additive and ad-valorem transport costs
	\end{tablenotes}
\end{table}

@@

\textbf{LP pour Guillaume: Changer les légendes pour les aligner sur la terminologie du papier, fitted vs unfitted.}

\begin{figure}[htbp]
\caption{Characterizing the time trends: applying Hummel's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
%{\small (A) Ad-valorem air freight} & {\small (B) Ad-valorem vessel freight}\\
%\multicolumn{2}{c}{{\small In percent of the export price}} \\
%\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.jpg}
%& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.jpg} \\
{\small (c) Ad-valorem air freight} & {\small (d) Ad-valorem vessel freight}\\
\multicolumn{2}{c}{{\small As indices with reference value 100 in 1974} }\\
\includegraphics[width=2.5in, height=2in]{figure5_comme_hummels_base100.jpg}
& \includegraphics[width=2.5in,height=2in]{figure6_comme_hummels_base100.jpg} \\
\end{tabular}
	\begin{minipage}  [c]  {6in}
		\scriptsize
\textbf{A AJUSTER SELON LEGENDE FINALE}.
\end{minipage}
\end{center}
\end{figure}

@@

Fourth, we differ in the weighting scheme retained to obtain the yearly value of the fitted transport cost (in the terms of \cite{hummels2007} method, the switch from $\widehat{TC}_{ikt}$ to $\widehat{TC}_{t}$, Equations (\ref{eq:comp_effects_adv}) and (\ref{eq:comp_effects_add}) in our case).
\cite{hummels2007} takes the unweighted average value over the $i,k$ dimension, which implicitly attributes a weight equal to 1 to each flow.
We proceed differently, as we weight each flow by its relative value on total trade flows (on the relevant year of observation), based on the argument that this weighting scheme does not overweight the small flows in value. However, we ensure that our results are not sensitive to an alternative weighting scheme, by building the average fitted transport costs rate as in \cite{hummels2007}, as reported in the following Section \ref{app:compeffects_weights}.

@@

The comparison of Figure \ref{fig:compeffects_robustness} (applying Hummel's weighting scheme) and Figure \ref{fig:totalTC_compeffects_excl} (applying our weighting scheme) prompts two comments.
First, differences do show up, in particular for the multiplicative component of air transport.
This suggests that the weighting scheme is not innocuous in the time trend decomposition exercise.
However, Figure \ref{fig:compeffects_robustness} also shows that the composition effects have contributed to strengthen the decrease in the ``ceteris paribus'' transport costs in air transport (in Figure \ref{fig:compeffects_robustness}, panel (A), overall transport costs have decreased more than the fitted component). This stands in accordance with the conclusions drawn from Figure \ref{fig:totalTC_compeffects_excl}, rather than partly offsetting this decline, as argued by \cite{hummels2007}. These results confirm that it is the functional form and precisely the modeling of the additive component, rather than the weighting scheme, that is key in understanding the underlying determinants of the overall transport costs time trends, as pointed out in Section \ref{sec:results_trends}.

>>>>

\textbf{XXX JH : I WOULD DELETE EVERYTHING FROM `` It is true that"- LP, OK METTRE EN SECTION 3 Comparaison des resultats XXX }

@@

Our analysis of transportation costs consists of exploiting the difference between commodity-level export and import prices, as in \cite{hummels2007}. The database we use to construct our measure of transport costs comes from the US annual ``Imports of Merchandise'' provided by the US Census Bureau, spanning 1974 to 2019 (details on the database provided in Appendix \ref{app:data}). We first use customs values, quantities and freight costs to recover free alongside ship (fas) and cost-insurance-freight (cif) prices, by good, country of origin and transportation mode.\footnote{The related literature commonly refers to the fob (free on board) price rather than the fas price. While both terms are closely related (see more details in Appendix \ref{app:data}), the US Foreign Trade Statistics reports fas prices.} More precisely, the (unit) fas price is computed as the total ``customs value'' in the US trade statistics divided by the shipping weight, both items being conditional to the transport mode; in other words, it is the price for one kg of the goods net of transportation costs, by transport mode.\footnote{One may be concerned by the fact that unit prices are calculated as the value divided by the shipping weight, rather than to the quantity (the number) of goods. This is due to the fact that in the Census data, information on the quantity of goods is not mode-specific. We yet provide a robustness check where unit values are built as the ratio between value and quantity of goods per observation, on a specific sub-sample restricted to US imports flows that only use one single transport mode. \textbf{See Section D.4 in the Online Appendix}. \textbf{XXX LE METTRE EN FOOTNOTE ME PARAIT LEGER, POINT IMPORTANT DU REFERE 1 + bcp de footnotes. Le remonter dans le corps PPL? XXX }} The cif price is then computed as the sum of the customs value and freight charges, once again divided by the shipping weight. Our dependant variable is finally computed as the ratio of the cif price divided by the fas price. By construction higher than 1, the variable provides a measure of transport costs as a proportion of the goods' price, an ad-valorem equivalent. This is quite a standard and widespread strategy, as emphasized by \cite{anderson_wincoop_jel}.

@@

As detailed below, the use of a non-linear estimator triggers computational limitations that limit the level of possible detail, especially when covering a long period of time. This drives us to estimate international transport costs at the 3-digit classification level, exploiting heterogeneity between products at the SITC-5 classification level. Depending on the year, this leaves us with around 200 3-digit sectors, from around 200 countries of origin (hence, around 400 fixed effects). We ensure the robustness of these results by conducting two types of alternative estimates: \textit{i),} within each 3-digit sector, exploiting heterogeneity between HS-10 products. Notice that this can be done from 1989 onwards for which HS-10 data are available; \textit{ii),} running the estimation at the 4-digit sector level (still with 5-digit products) for some selected years. The selected years for the 4-digit level estimations are: 1974, 1977, 1981, 1985, 1989, 1993, 1997, 2001, 2005, 2009, 2019. Comparing different levels of aggregation is useful to check differences and the presence of biases precisely due to aggregation. However, we obtain no substantial difference between the results obtained for the benchmark 3-5 sector-product classification levels and those considering either the 3-10 and 4-5 ones (See Table \ref{tab:summary_results} and Section B of the online appendix for the 4-5 results; and Table \ref{tab:baseline10}, Section \ref{sec:robustness} for the 3-10 estimation results).

@@

\paragraph{The share of additive costs: Time dynamics} As next step, we investigate whether additive costs are a long-lasting, i.e. a structural phenomenon. Figure \ref{fig:part_cout_additif} reports the share of additive costs in total transport costs on a yearly basis, in both air and vessel transport, based on the weighted-mean values $\widehat{t}/\widetilde{p}$ and $\widehat{\tau}$.

@@

Three main comments can be made. First, the subset of large trade flows we are considering (around 8\% of the observations of our initial sample, but the vast majority of the total value of aggregated trade, with an annual mean of 68\%) involve a higher share of additive costs: between 48\% and 55\% of total costs on average, versus 30\% to 44\% on the whole sample.
%JH: la phrase suivante est en contradiction avec celle qui suit encore juste après: "Second, assuming that country/product fixed effects are separable in these two dimensions tends to overestimate the value and the share of the additive costs."
Second, both models provide a similar quality of fit of the regression (once we take into account the number of right-hand-side variables) as the AIC criteria display very close values in both models (conditional on transport mode). Third, crucially for this robustness check the estimated values remain of similar magnitude under both separability and non-separability assumptions.\footnote{We also run two other robustness checks: \textit{i}) comparing the results with/without the separability assumption on a yearly basis and \textit{ii}) reporting the histogram of the distribution for $\beta$ over the triplet $(i,k,t)$, which confirm the robustness of the results. These results are reported in the Online Appendix, Section C. \textbf{XXX ENLEVER LA PARTIE SUR LE LIEN BETA-SEPARABILITE EN ANNEXE ET AJUSTER FOOTNOTE XXX}} %, even if one can note that under the separability assumption, the share of additive costs seems slightly biased upward, at least for averages over the period. The picture is reversed for medians

@@

\begin{figure}[htbp]
\caption{Transport cost time trends: robustness to IV procedure}
\label{fig:comp_IV_SITC5}
\begin{center}
\includegraphics[height=8cm]
{scatter_chronology_baseline_IV_ref1_y_5_3.png}
\end{center}
\end{figure}
%viens de comparaison.do

@@

Yet, as Table \ref{tab:baseline10} and 	Figure \ref{fig:robustness_to_agregation} show, the results are very similar when using 10-digit product and 5-digit products. If anything, the $\beta$ seems on average slightly higher when estimated based on a 3 (sector)-10 (product) database, indicating a (small) downward bias in our estimates of additive costs. But overall, no major difference arises both regarding levels and trends - results are especially very close for the Air transportation mode. This has important implications for the exercise performed in Section \ref{sec:theory}: welfare gains computations should not be significantly affected by our use of 3 (sector)-5 (product) digit data. This is consistent with e.g. \citet{Giri_et_al2021}, who show that sectoral heterogeneity does not always lead to an increase in the gains from trade.

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: Robustness to aggregation (2005-2019)} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10_reshaped.tex}
	\begin{tablenotes}
		\scriptsize
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
        \item Transport costs expressed in \% of the fas price (except for $\widehat{t}$ expressed in USD.
		%\item \textbf{Model (A): With ad-valorem transport costs only}
		\item Model (B): With additive and ad-valorem transport costs
	\end{tablenotes}
\end{table}

@@

\begin{figure}[htbp]
\caption{Characterizing the time trends: Applying Hummels's (2007) method }
\label{fig:comp_effects_as_in_Hummels}
\begin{center}
\begin{tabular}{cc}
%{\small (A) Ad-valorem air freight} & {\small (B) Ad-valorem vessel freight}\\
%\multicolumn{2}{c}{{\small In percent of the export price}} \\
%\includegraphics[width=2.5in, height=1.8in]{figure5_comme_hummels.jpg}
%& \includegraphics[width=2.5in,height=1.8in]{figure6_comme_hummels.jpg} \\
{\small (c) Air } & {\small (d) Vessel}\\
\includegraphics[width=2.5in, height=2in]{figure5_comme_hummels_base100.jpg}
& \includegraphics[width=2.5in,height=2in]{figure6_comme_hummels_base100.jpg} \\
\end{tabular}
	\begin{minipage}  [c]  {5in}
		\footnotesize
Total transport costs expressed in percentage of the value shipped, then built as indices with reference value 100 in 1974.
\end{minipage}
\end{center}
\end{figure}

@@

Fourth, we differ in the weighting scheme retained to obtain the yearly value of the fitted transport cost (in the terms of \cite{hummels2007} method, the switch from $\widehat{TC}_{ikt}$ to $\widehat{TC}_{t}$). \cite{hummels2007} takes the unweighed average value over the $i,k$ dimension, which implicitly attributes a weight equal to 1 to each flow. We proceed differently, as we weight each flow by its relative value on total trade flows (on the relevant year of observation), based on the argument that this weighting scheme does not overweight the small flows in value. However, we ensure that our results are not sensitive to an alternative weighting scheme, by building the average fitted transport costs rate as in \cite{hummels2007}, as reported in the following Section \ref{app:compeffects_weights}.

@@

The comparison of Figure \ref{fig:compeffects_robustness} (applying Hummels's weighting scheme) and Figure \ref{fig:totalTC_compeffects_excl} (applying our weighting scheme) prompts two comments.
First, differences do show up, in particular for the multiplicative component of air transport.
This suggests that the weighting scheme is not innocuous in the time trend decomposition exercise.
However, Figure \ref{fig:compeffects_robustness} also shows that the composition effects have contributed to strengthen the decrease in the ``ceteris paribus'' transport costs in air transport (in Figure \ref{fig:compeffects_robustness}, panel (A), overall transport costs have decreased more than the fitted component). This stands in accordance with the conclusions drawn from Figure \ref{fig:totalTC_compeffects_excl}, rather than partly offsetting this decline, as argued by \cite{hummels2007}. These results confirm that it is the functional form and precisely the modeling of the additive component, rather than the weighting scheme, that is key in understanding the underlying determinants of the overall transport costs time trends, as pointed out in Section \ref{sec:results_trends}.
